%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Institute for Aerospace Studies{\enskip\cdotp\enskip}Space and Terrestrial Autonomous Robotic Systems (STARS) Lab} % Degree
    {Doctor of Philosophy {\enskip\cdotp\enskip}University of Toronto} % Institution
    {Toronto, Canada} % Location
    {2014 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis title: ``On learning models of appearance for robust long-term visual navigation.'' Advised by Prof. Jonathan Kelly.}
        \item {Supported by an NSERC Postgraduate Scholarship - Doctoral Program, valued at \$63,000.}
        \item {Only Canadian invited to participate in the first annual RSS Pioneers workshop and mentor junior students as part of Inclusion@RSS.}
        \item {Appointed as a Postgraduate Affiliate of the Vector Institute.}
      \end{cvitems}
    }

  \cventry
    {Institute for Aerospace Studies{\enskip\cdotp\enskip}Space and Terrestrial Autonomous Robotic Systems (STARS) Lab} % Degree
    {M.A.Sc. (Partial), Aerospace Science \& Engineering {\enskip\cdotp\enskip}University of Toronto} % Institution
    {Toronto, Canada} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 4.0 / 4.0}
        \item {Transferred directly to the Ph.D. program without completing the M.A.Sc. thesis.}
        \item {Supported by an NSERC Canada Graduate Scholarship - Master’s Program, valued at \$21,000.}
        \item {Received a Kenneth Molson Fellowship, valued at \$12,000.}
      \end{cvitems}
    }

  \cventry
    {Department of Physics and Astronomy{\enskip\cdotp\enskip}Department of Computer Science} % Degree
    {B.Sc. (Maj.) with Distinction, Physics \& Computer Science{\enskip\cdotp\enskip}University of Manitoba} % Institution
    {Winnipeg, Canada} % Location
    {2010 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 4.31 / 4.50}
        \item {Received two competitive Centennial Scholarships in Physics in 2011 and 2012.}
        \item {Received two NSERC Undergraduate Student Research Awards in 2012 and 2013.}
      \end{cvitems}
    }

  \cventry
    {I. H. Asper School of Business} % Degree
    {B.Comm. (Hon.) with Distinction, Accounting \& Finance{\enskip\cdotp\enskip}University of Manitoba} % Institution
    {Winnipeg, Canada} % Location
    {2006 - 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {GPA: 4.13 / 4.50}
        \item {Inducted into Beta Gamma Sigma Honors Society.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
