%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineering{\enskip\cdotp\enskip}Prediction Team} % Job title
    {Lead Software Engineer (Prediction) {\enskip\cdotp\enskip}Oxbotica} % Organization
    {Toronto, Canada} % Location
    {2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leading design, development and analysis of motion prediction algorithms for on- and off-road mobile autonomy.}
        \item {Ensuring quality and correctness of production-level C++ code produced by my team.}
        \item {Planning, executing and reporting against team- and company-level technical roadmaps using JIRA and other tools.}
        \item {Coordinating across teams to deliver on complex software development projects.}
        \item {Supporting personal and professional development of my team members.}
      \end{cvitems}
    }

  \cventry
    {Engineering{\enskip\cdotp\enskip}Object Tracking \& Prediction Team} % Job title
    {Software Engineer{\enskip\cdotp\enskip}Oxbotica} % Organization
    {Toronto, Canada} % Location
    {2019 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed model- and learning-based object tracking and prediction algorithms for on- and off-road mobile autonomy.}
      \end{cvitems}
    }
  
  \cventry
    {Institute for Aerospace Studies{\enskip\cdotp\enskip}Space and Terrestrial Autonomous Robotic Systems (STARS) Lab} % Job title
    {Graduate Researcher{\enskip\cdotp\enskip}University of Toronto} % Organization
    {Toronto, Canada} % Location
    {2013 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted independent research on improving model-based visual navigation systems using modern machine learning techniques.}
        \item {Developed, tested and published a neural network sun sensor to correct long-range drift errors in visual odometry.}
        \item {Developed, tested and published learning-based image transformations to aid visual localization under appearance change.}
      \end{cvitems}
    }
    
  \cventry
    {Self-Driving Cars Specialization{\enskip\cdotp\enskip}University of Toronto} % Job title
    {Subject Matter Expert{\enskip\cdotp\enskip}Coursera} % Organization
    {Toronto, Canada} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-created the State Estimation and Localization course of the Coursera Self-Driving Cars Specialization.}
      \end{cvitems}
    }
    
  \cventry
    {Division of Engineering Science} % Job title
    {Course Instructor{\enskip\cdotp\enskip}University of Toronto} % Organization
    {Toronto, Canada} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AER 521: Mobile Robotics and Perception}
        \item {ROB 501: Computer Vision for Robotics}
      \end{cvitems}
    }

  \cventry
    {Division of Engineering Science} % Job title
    {Teaching Assistant{\enskip\cdotp\enskip}University of Toronto} % Organization
    {Toronto, Canada} % Location
    {2015 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {ROB 301: Introduction to Robotics}
        \item {AER 521: Mobile Robotics and Perception}
      \end{cvitems}
    }


  \cventry
    {Argonne National Laboratory Physics Division{\enskip\cdotp\enskip}University of Manitoba Department of Physics and Astronomy} % Job title
    {Research Assistant{\enskip\cdotp\enskip}Argonne National Laboratory} % Organization
    {Chicago, USA} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in experiments with the Argonne Tandem Linac Accelerator System (ATLAS).}
%        \item {Supervised by Prof. Kumar Sharma and Dr. Jason Clark.}
      \end{cvitems}
    }
  
    \cventry
    {Department of Physics and Astronomy} % Job title
    {Research Assistant{\enskip\cdotp\enskip}University of Manitoba} % Organization
    {Winnipeg, Canada} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed astrophysical modelling software.}
%        \item {Supervised by Prof. Jason Fiege.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
